smooth-sea

### 2018-05-27 index.rmd
close to ready to go

@@

sea_df <- panel %>% #set to NA for INLA to forecast
  mutate(actualRent = med1B,
         med1B = ifelse(listingQtr == as.yearqtr(Sys.Date()), NA, med1B)) %>%
  dplyr::select(GISJOIN, listingQtr, Qtr, medRent, med1B, lagRent, actualRent, nHU,
                n1B, nListings, pOwnoccHU, medHUVal, idtract) %>%
  mutate(p1B = n1B/nListings) %>%
  arrange(listingQtr, GISJOIN)

@@

#create neighbor file that INLA takes for hyperparameter args
nb2INLA("./output/seatract.graph", sea_adj)
sea_df$idqtr <- factor(sea_df$listingQtr, ordered = T)
sea_df$idqtr1 <- sea_df$idqtr
sea_df$idtractqtr <- paste(sea_df$idtract, sea_df$idqtr)
sea_df$idtract1 <- sea_df$idtract

@@

#spatial random effect model (BYM 1991) with seasonal dummies
form.bym <- log(med1B) ~ 1 + Qtr +
  f(idtract, model = "bym", #ICAR spatial RE for tract neighbors + IID RE for tract
    scale.model = T,
    graph = "./output/seatract.graph")

@@

#spatio-temporal smoothing model, AR(1) process with linear space-time interaction (Bernadelli 1995)
form.spt <- log(med1B) ~ 1 +
  f(idtract, model = "bym", #ICAR spatial RE for tract neighbors + IID RE for tract
    scale.model = T,
    graph = "./output/seatract.graph") +
  f(idqtr, model = "ar1") +
  f(idqtr1, model = "iid") +
  f(idtractqtr, model = "iid")

@@

sea_df

>>>>

#load demo extract
#demo <- read_csv(file = "./input/tractDemoSumStats.csv")

#load culture extract
#culture <- read_csv(file = "./input/tractCultureSumStats.csv")

#load police report extract
#police <- read_csv(file = "./input/tractPoliceReportSumStats.csv")

@@

#panel <- left_join(panel, demo)
#panel <- left_join(panel, culture)
#panel <- left_join(panel, police)
#panel <- left_join(panel, sea_shp@data)

sea_df <- panel %>% #set to NA for INLA to forecast
  mutate(actualRent = med1B,
         med1B = ifelse(listingQtr == as.yearqtr(Sys.Date()), NA, med1B)) %>%
  mutate(p1B = n1B/nListings) %>%
  arrange(listingQtr, GISJOIN)

@@

#create neighbor file that INLA takes for hyperparameter args
nb2INLA("./output/seatract.graph", sea_adj)
sea_df$idqtr <- factor(sea_df$listingQtr, ordered = T)
sea_df$idqtr1 <- sea_df$idqtr
sea_df$idtractqtr <- paste(sea_df$idtract, sea_df$idqtr)
sea_df$idtract1 <- sea_df$idtract
sea_df$Qtr1 <- sea_df$Qtr

@@

#spatial random effect model (BYM 1991) with seasonal dummies
form.bym <- log(med1B) ~ 1 + Qtr +
  f(idqtr, model = "iid") +
  f(idtract, model = "bym", #ICAR spatial RE for tract neighbors + IID RE for tract
    scale.model = T,
    graph = "./output/seatract.graph")

@@

#spatio-temporal smoothing model, AR(1) process with linear space-time interaction (Bernadelli 1995)
form.spt <- log(med1B) ~ 1 +
  f(idtract, model = "bym", #ICAR spatial RE for tract neighbors + IID RE for tract
    scale.model = T,
    graph = "./output/seatract.graph") +
  f(idqtr, model = "ar", order = 1) +
  f(idtractqtr, model = "iid")

@@
